---
title: "R Notebook"
output: html_notebook
---
https://www.usna.edu/Users/oceano/pguth/md_help/html/tbme6h0z.htm
```{r setup}
library(sf)
library(stars)
library(xml2)
library(flatxml)
```

```{r}
dir.create("kml")
zipF<- "baronskogenelg.kmz"
outDir<-"kml/"
unzip(zipF,exdir=outDir)
```


```{r}
doc.kml <- read_xml("kml/doc.kml")

jpg <- xml_text(xml_find_all(doc.kml, ".//d1:href", xml_ns(doc.kml)))
north <- xml_text(xml_find_all(doc.kml, ".//d1:north", xml_ns(doc.kml)))
south <- xml_text(xml_find_all(doc.kml, ".//d1:south", xml_ns(doc.kml)))
east <- xml_text(xml_find_all(doc.kml, ".//d1:east", xml_ns(doc.kml)))
west <- xml_text(xml_find_all(doc.kml, ".//d1:west", xml_ns(doc.kml)))
rotation <- xml_text(xml_find_all(doc.kml, ".//d1:rotation", xml_ns(doc.kml)))
file_name <- substr(jpg, 7, 24)
df <- data.frame(jpg,north,south,east,west,rotation,file_name)           
```
World file contents
The contents of the world file will look something like this:

20.17541308822119
0.00000000000000
0.00000000000000
-20.17541308822119
424178.11472601280548
4313415.90726399607956

Note: values cannot be in scientific notation.
The values are inputs into the following formulas:

x1 = Ax + By + C
y1 = Dx + Ey + F

where the variables represent the following:

x1 = calculated x-coordinate of the pixel on the map
y1 = calculated y-coordinate of the pixel on the map
x = column number of a pixel in the image
y = row number of a pixel in the image
A = x-scale; dimension of a pixel in map units in x direction
B,D = rotation terms
C,F = translation terms; x,y map coordinates of the center of the upper-left pixel
E = negative of y-scale; dimension of a pixel in map units in y direction
The y-scale (E) is negative because the origins of an image and a geographic coordinate system are different. The origin of an image is located in the upper-left corner, whereas the origin of the map coordinate system is located in the lower-left corner. Row values in the image increase from the origin downward, while y-coordinate values in the map increase from the origin upward.

The transformation parameters are stored in the world file in this order:

20.17541308822119 = A
0.00000000000000 = D
0.00000000000000 = B
-20.17541308822119 = E
424178.11472601280548 = C
4313415.90726399607956 = F

```{r}

file_list <- list.files("kml", pattern = "*.jpg", recursive = T, full.names = T)
for (file in file_list) {
  tmp <- raster::raster(file)
  file_name_out <- substr(file, 11, 28)
  tmp1 <- df %>% filter(file_name_out == file_name)
  lon1 <- as.numeric(as.character(tmp1$south[1])) 
  print(lon1)
  lon2 <- as.numeric(as.character(tmp1$north[1]))
  print(lon2)
  lat1 <- as.numeric(as.character(tmp1$east[1]))
  print(lat1)
  lat2 <- as.numeric(as.character(tmp1$west[1]))
  print(lat2)
  rotation <- as.numeric(as.character(tmp1$rotation[1]))
  xsize = dim(tmp)[1]
  print(xsize)
  ysize = dim(tmp)[2]
  print(ysize)
  if (lon1 < lon2) {
    t = lon1
    lon1 = lon2
    lon2 = t
  }

  if (lat1 > lat2) {
    t = +lat1
    lat1 = lat2
    lat2 = t
  }
# dimX=$(echo "($east-($west))/$width" | bc -l)
# dimY=$(echo "($south-($north))/$height" | bc -l)
  ppx = (lon1 - lon2) / xsize
  ppy = (lat1 - lat2) / ysize
print(ppx)
print(ppy)
  
  cat(
    ppx,
    "0",
    "0", #rotation,
    ppy,
    lat2 = lat2 + (ppy / 2), # // y center of pixel
    lon2 = lon2 + (ppx / 2), # // x center of pixel
    file = paste0("kml/files/", file_name_out, ".jgw"),
    sep = "\n",
    append = F
  )
}
# C=$(echo "$west+($dimX/2)" | bc -l)
# F=$(echo "$north+($dimY/2)" | bc -l)
```


